---
title: "SERRF"
author: "George GUO"
date: "25/01/2021"
output:
  html_document: 
    keep_md: yes
    toc: yes
    toc_float: yes
    collapsed: no
    theme: spacelab
    number_sections: yes
    highlight: zenburn
    fig_width: 10
    fig_height: 10
    df_print: tibble
  pdf_document: default
  word_document: default
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
source("Randomforest.R")
source("Parallele.R")

Combine_result_file<-function(path){
  
  e=read.csv(paste0(path,"/","e.csv"),stringsAsFactors = F)
  
  enorm=read.csv(paste0(path,"/","SERRF_normalized.csv"),stringsAsFactors = F)
  
  f=read.csv(paste0(path,"/","f.csv"),stringsAsFactors = F)
  
  p=read.csv(paste0(path,"/","p.csv"),header = F,stringsAsFactors = F)
  
  p=p[,2:5]
  
  
  
  rownames(p)=as.character(p[,which(p[1,]=="time")])
  rownames(p)[1]="time"
  tp=as.data.frame(t(p),stringsAsFactors=F)
  colnames(e)=as.character(p[,which(p[1,]=="time")])
  finaltable<-rbind(tp,e)
  colnames(enorm)=as.character(p[,which(p[1,]=="time")])
  finaltablenorm<-rbind(tp,enorm)
  
  return(list(raw=finaltable,norm=finaltablenorm))
  
  
}
```

## data preparation

Place the attachments to the same folder and run the "Knit".


Now we run the script to analyze a GC-MS data set.

## Load data
```{r cars}
#data<-readData_serrf_native(path =  "GC-MS Result(PeakArea).csv",infopath="subject_information_sheet.csv")

data<-readData(path = "Area_7_20192281555.txt_output.csv")
```
Loaded data has three components:
e, f, p

e contains the response data:
```{r}
data$e
```


f is the summary of all considered features:
```{r}
data$f
```
p is the summary of all samples, time is the injection order:
```{r}
data$p
```

So you may need to prepare your data into these format as well.

## Run Serrf

You can also embed plots, for example:

```{r , eval=FALSE, include=T}


SERRF_Norm_finaltable<-SERRF(data=data,Log_trans=F,zero_imputaion=T,vis_norm_result=F,Predict_level="QC")


```

## view the results
browser to the sub-folder to have a look at the normed results:
```{r}
library(magick)
p<-image_read(paste0("Area.csvSERRF_QC/combine_figure.png"))
p

```

Or the normed results of some representative features:
```{r}
library(magick)
p<-image_read(paste0("Area.csvSERRF_QC/combine_figure_pcs.png"))
print(p)

```
